Detecting Facial Expressions in Professional Tennis Matches

### 2017-02-24 Report06-12.Rmd
Fixed face box outside of range bug.

    p <- ggplot(data.frame(x=c(0,800), y=c(0,450)), aes(x,y)) +
      theme_void()+ coord_fixed()+
      annotation_custom(rasterGrob(img)) +
      scale_x_continuous(expand = c(0,0), limits = c(0,800)) +
      scale_y_continuous(expand = c(0,0), limits = c(0,450))

>>>>

    p <- ggplot(data.frame(x=c(0,800), y=c(0,450)), aes(x,y)) +
      theme_void()+ coord_fixed()+
      annotation_custom(rasterGrob(img)) +
      coord_cartesian(xlim=c(0, 800), ylim=c(0,450))
